quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-05 paper-quollr.Rmd
Add different representations for prism data

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggbeeswarm)
library(patchwork)
library(Rtsne)
library(readr)
library(tools)
library(cardinalR)

@@

<!--add intro to prism data-->

@@

<!-- how the data are generated and from which package I got the data-->

@@

<!--added, I selected tSNE with perplexity = 35 to explore and -->

```{r}
sc_ltr_pos <- c(0.08, 0.96)

tSNE_fit <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = round(sqrt(NROW(triangular_3d_data))))

@@

nldr_prism1 <- tsne_prism_scaled |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5)

nldr_prism1
```

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(ggbeeswarm)
library(patchwork)
library(Rtsne)
library(uwot)
library(readr)
library(tools)
library(cardinalR)

@@

@@

@@

```{r}
sc_ltr_pos <- c(0.08, 0.96)
```

<!--tSNE with perplexity = 35-->
```{r}
tSNE_fit <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = round(sqrt(NROW(triangular_3d_data))))

@@

nldr_prism1 <- tsne_prism_scaled |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

```{r}
tSNE_fit2 <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = 6)

tsne_prism2 <- tSNE_fit2$Y |>
  as_tibble() |>
  mutate(ID = row_number())

colnames(tsne_prism2) <- c("tSNE1", "tSNE2", "ID")

prism_scaled_obj2 <- gen_scaled_data(
  data = tsne_prism2)
tsne_prism_scaled2 <- prism_scaled_obj2$scaled_nldr

nldr_prism2 <- tsne_prism_scaled2 |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

```{r}
tSNE_fit3 <- triangular_3d_data |>
  select(-ID) |>
  Rtsne(perplexity = 58)

tsne_prism3 <- tSNE_fit3$Y |>
  as_tibble() |>
  mutate(ID = row_number())

colnames(tsne_prism3) <- c("tSNE1", "tSNE2", "ID")

prism_scaled_obj3 <- gen_scaled_data(
  data = tsne_prism3)
tsne_prism_scaled3 <- prism_scaled_obj3$scaled_nldr

nldr_prism3 <- tsne_prism_scaled3 |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

<!--UMAP with n_neighbors = 35-->
```{r}
umap_pbmc <- triangular_3d_data |>
  select(-ID) |>
  umap(n_neighbors = 35, n_components =  2, 
       metric = "euclidean", min_dist = 0.5, init = "spca")

umap_pbmc <- umap_pbmc |>
  as_tibble()

names(umap_pbmc) <- c("UMAP1", "UMAP2")

umap_pbmc <- umap_pbmc |>
  mutate(ID = 1:NROW(umap_pbmc))

nldr_prism4 <- umap_pbmc |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

```{r}
umap_pbmc2 <- triangular_3d_data |>
  select(-ID) |>
  umap(n_neighbors = 15, n_components =  2, 
       metric = "euclidean", min_dist = 0.01, init = "spca")

umap_pbmc2 <- umap_pbmc2 |>
  as_tibble()

names(umap_pbmc2) <- c("UMAP1", "UMAP2")

umap_pbmc2 <- umap_pbmc2 |>
  mutate(ID = 1:NROW(umap_pbmc))

nldr_prism5 <- umap_pbmc2 |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

```{r}
umap_pbmc3 <- triangular_3d_data |>
  select(-ID) |>
  umap(n_neighbors = 69, n_components =  2, 
       metric = "euclidean", min_dist = 0.6, init = "spca")

umap_pbmc3 <- umap_pbmc3 |>
  as_tibble()

names(umap_pbmc3) <- c("UMAP1", "UMAP2")

umap_pbmc3 <- umap_pbmc3 |>
  mutate(ID = 1:NROW(umap_pbmc))

nldr_prism6 <- umap_pbmc3 |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) 
```

```{r}
nldr_prism1 + nldr_prism2 + nldr_prism3 + 
  nldr_prism4 + nldr_prism5 + nldr_prism6 +
  plot_layout(ncol=3)
```
